---
title: "Transformation Initiatives Management Tool"
author: "Fatimah Abuali"
date: "2022-09-17"
output:
  html_document:
    toc: yes
    number_section: yes
    toc_float: yes
  theme: Cayman
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

**TIM** is a tool to meet the needs of planning and deploying strategic initiatives during the transition journey.

To align goals, initiatives, projects & actions to drive performance and profitability

**TIM** provides a simple, centralized method to manage and collaborate on programs and projects that are linked to strategic initiatives and objectives.

-   Connection between planning & execution

-   Consistency in working on actions/projects that are linked back to transformation strategy and initiatives

-   Adequate communications between departments/levels

```{r cars}
summary(cars)
```

## Problem Statement

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Framework

### Proposed Project Management Life Cycle Wave 1

#### Processes and RACI

![](images/DTO.pptx%20(2).jpg)

## Methodology and Design

#### Project/Initiative Management Level

![](images/DTO.pptx%20(3).jpg)

#### Data Extraction into Real-time Data-sets in Master database

![](images/DTO.pptx%20(4).jpg)
